Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-16 WSSSPE3/report/wg_appendix_eng_design.tex
Update wg_appendix_eng_design.tex
Minor updates to sub-sections

\subsection{Key Next Steps}

\subsection{Plan for Future Organization}
The following plan for future organization was discussed:
\begin{itemize}
\item Identify suitable undergraduate or post-graduate students.
\item Organizing coordinating online calls via Google Hangout.
\end{itemize}

\subsection{What Else is Needed?}
The following list of what else is required :

\begin{itemize}
\item Ethic committee approval required for data collection.
\end{itemize}

>>>>

\subsection{Key Next Steps}
In order to achieve (1) the systematic analysis a number of example systems from different scientific domains with regards to the identified principles, (2) the identification of the commonalities and gaps in applying principles to different scientific systems, and (3) the proposal of a set of guidelines on the principles, the following next steps were discussed:

\subsection{Plan for Future Organization}
The following plan for future organization was discussed:
\begin{itemize}
\item Identify suitable undergraduate or post-graduate students.
\item Design and pilot study.
\item Organizing coordinating online calls via Google Hangout.
\end{itemize}

\subsection{What Else is Needed?}
The following list of what else is required :
\begin{itemize}
\item Ethics committee review panel approval required for data collection.
\end{itemize}
